---
title: "NYC Motor Vehicle Collision Crashes Logistic Regression Analysis"
author: "Jordan Wong"
date: "2023-01-16"
output: html_document
---

### First, clear all previous stuff out of the workplace...
```{r}
rm(list = ls());
```

### Input dataset
```{r}
mydata <- read.csv("Motor_Vehicle_Collisions_Crashes_log.csv",header=TRUE)
```

### Fit the model to the data by creating a formula and passing it to the glm function. 
### I created a new column and use it as a dummy variable because I want to find out the relationship between each variables and the y. this column will indicate if there are any death occur in crashes.
```{r}
fit = glm(People_died ~ factor(Crashes_by_month) + factor(Crash_Time) + factor(BOROUGH) +                          factor(Ten_Most_Common_Factor) + Two_Factors + Three_Factors + Four_Factors + Five_Factors +             factor(Ten_Most_Vehicle_Type) + Two_cars + Three_Cars + Four_Cars + Five_Cars, data = mydata,            family=binomial(link = "logit"))
```

### Invoke the summary function to see the results
```{r}
summary(fit)
```
### Regression diagnostic 1
### To make sure the model does not have multi-collinearity issue, we check the correlation between each two explanatory variables
### Caculate correlation matrix
```{r}
correlation <- cor(mydata)
round(correlation, 2)
```
### Regression diagnostic 2
### Model specification errors?
### The model does not exclude any "core" variables.
### The model does not include superfluous variables.
### The functional form of the model is suitably chosen.
### There are no errors of measurement in the regressand and regressors.
### Outliers in the data, if any, are taken into account
```{r}
summary(mydata)
```

### Turn off output
```{r}
sink();
```

