---
title: "NYC Motor Vehicle Collisions Crashes Linear Regression Analysis"
author: "Jordan Wong"
date: "2023-01-16"
output: html_document
---

### First, clear all previous stuff out of the workspace...
```{r}
rm(list = ls());
```

### Import the dataset file
```{r}
mydata <- read.csv("Motor_Vehicle_Collisions_Crashes.csv",header=TRUE)

```

### We fit the model with the dataset "mydata"
```{r}
mfit <- lm(NUMBER_OF_PERSONS_KILLED ~ factor(Crash_Time) + factor(Crashes_by_month) + factor(BOROUGH) +             factor(Ten_Most_Common_Factor) + Two_Factors + Three_Factors + Four_Factors + Five_Factors +             factor(Ten_Most_Vehicle_Type) + Two_cars + Three_Cars + Four_Cars + Five_Cars, data = mydata)
```

### Check the summary
```{r}
summary(mfit)
```

### Regression diagnostic 1
### To make sure the model does not have multi-collinearity issue, we check the correlation between each two explanatory variables
### Caculate correlation matrix
```{r}
correlation <- cor(mydata)
round(correlation, 2)
```

### Regression diagnostic 2
### To make sure the model does not have the issue of heteroscedasticity in the error term, we do the Breusch Pagan Test.
```{r}
if (!require("lmtest")) { install.packages("lmtest")
  require("lmtest") }
bptest(mfit)
```

### Regression diagnostic 3
### Model specification errors?
### The model does not exclude any "core" variables.
### The model does not include superfluous variables.
### The functional form of the model is suitably chosen.
### There are no errors of measurement in the regressand and regressors.
### Outliers in the data, if any, are taken into account.
```{r}
summary(mydata)
```
### The probability distribution of the error term is well specified.
```{r}
if (!require("nortest")) { install.packages("nortest")
  require("nortest") }
res=residuals(mfit)
ad.test(res)$p.value
```
### Turn off output
```{r}
sink();
```
